Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being\thanks{Code and data are available at: https://github.com/lucas11333/Of\_Wellbeing}

### 2023-04-06 outputs/paper/paper.tex
Add files via upload

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012},
  pdfauthor={SHAOHAN CHANG},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Exploring Relationships between Demographic Characteristics,
Health, Finances, Living Arrangements, and Happiness: An Analysis of the
General Social Survey (GSS) Data from 1972 to 2012\thanks{Code and data
are available at: https://github.com/lucas11333/Factor\_of\_Wellbeing}}
\author{SHAOHAN CHANG}
\date{28 March 2023}

\begin{document}
\maketitle
\begin{abstract}
This paper presents an analysis of a subset of the General Social Survey
(GSS) data from the year 1972, which includes information on
individuals' demographic characteristics, health, finances, living
arrangements, and subjective well-being. The study aimed to explore
various aspects of individuals' lives during the early 1970s in the
United States, such as social stratification, gender roles, family
dynamics, health disparities, and subjective well-being.The dataset
consists of 5 observations and 10 variables, including year, age, sex,
babies, divorce, health, finance\_satisfied, living\_area, and happy.
The study used graphical representation to analyze the relationships
between different variables in the dataset and individuals' level of
happiness. The results of the analysis suggest that there is a positive
relationship between people's satisfaction with their current financial
situation, their self-rated health, and their level of happiness in
life. Additionally, being divorced may have a slight impact on one's
level of happiness in life, with a small proportion of individuals
feeling not too happy. Moreover, the study found that people's level of
education is positively associated with their level of happiness in
life, as people's education level increases, their level of happiness
also gradually increases.Overall, this study provides valuable insights
into various aspects of individuals' lives during the early 1970s in the
United States. The findings can be useful for researchers and students
interested in exploring topics such as social stratification, gender
roles, family dynamics, health disparities, and subjective well-being.
The study highlights the importance of considering different factors
that can influence individuals' level of happiness and well-being, such
as their financial situation, health status, and level of education.
Further research could investigate more recent data from the GSS to
examine changes in these relationships over time.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Surveys are a common method for collecting data on individuals'
attitudes, behaviors, and experiences in social science research. One
such survey is the General Social Survey (GSS), which has been conducted
in the United States since 1972 to 2012. This data set is a subset of
the GSS data from the year 1972, which includes information on
individuals' demographic characteristics, health, finances, living
arrangements, and subjective well-being. While this is a relatively
small data set, it provides a glimpse into the lives of individuals in
the United States during a particular period in time.This paper aims to
explore various aspects of individuals' lives during the early 1970s in
the United States using the GSS data set. The variables in this data set
are diverse and reflect a range of aspects of individuals' lives. For
instance, the variables on babies and divorce provide information on
individuals' family structures, while the variables on health and
finance satisfaction offer insights into their well-being and financial
stability (Vlaev 2014). The data set also includes variables on
individuals' living arrangements and their subjective well-being,
providing a glimpse into their social context and overall happiness.

The paper presents a comprehensive analysis of the relationships between
different variables in the data set and individuals' level of happiness.
The analysis includes a graphical representation of the relationship
between the number of children and happiness in the family, individuals'
self-rated health and their self-rated level of happiness, people's
satisfaction with their financial situation and their happiness, the
level of happiness in life for individuals in two different states:
divorced or married, and the relationship between people's level of
education and their level of happiness in life.The results of the
analysis suggest that there is a positive relationship between people's
satisfaction with their current financial situation, their self-rated
health, and their level of happiness in life (RSiahpush 2008). The
analysis also indicates that being divorced may have a slight impact on
one's level of happiness in life, with a small proportion of individuals
feeling ``not too happy.'' Additionally, as people's education level
increases, their level of happiness also gradually increases.

Overall, this paper provides valuable insights into various aspects of
individuals' lives during the early 1970s in the United States. The
findings can be useful for researchers and students interested in
exploring topics such as social stratification, gender roles, family
dynamics, health disparities, and subjective well-being.

\hypertarget{methodology}{%
\subsection{Methodology}\label{methodology}}

This study will combine data sources, including surveys and academic
literature. The collected data will be analyzed to determine the trends
and changes in public attitudes towards sexual morality over time (1972
to 2012). The study will also examine differences in attitudes between
men and women, as well as work attitudes, and the relationship between
education levels and happiness in daily life.

@@

Used some R language packages, such as tidyverse (Wickham et al. 2019),
dplyr (Wickham et al. 2023), janitor (Firke 2023) , knitr (Xie 2014),
here (Müller 2020), haven (Wickham, Miller, and Smith 2022), ggplot
(Wickham 2016) , kableExtra (Zhu 2021) to assist in data analysis, and
the data from General Social Survey ({``GSS General Social Survey''}
2023).

\hypertarget{sec-data}{%
\subsection{Data}\label{sec-data}}

After cleaning the data and selecting the main variables, the following
table shows the first five rows of data and their corresponding
parameters.The following data section provides a more detailed
explanation of the selected variables for the data.

This data-set contains information on various personal and demographic
characteristics of individuals, collected between the years 1972 and
2012. The data-set includes variables such as age, sex, number of
babies, divorce status, self-reported health status, financial
satisfaction, living area, and level of happiness. The data-set can be
used to study the relationships between these variables and to gain
insights into factors that may influence an individual's overall life
satisfaction.

\begin{table}

\caption{Table of Happy by Various Variables}
\centering
\begin{tabular}[t]{r|l|l|l|l|l|l|l}
\hline
year & age & sex & babies & divorce & health & finance\_satified & living\_area\\
\hline
1972 & 70 & male & 0 & no & fair & more or less satisfied & large city\\
\hline
1972 & 48 & female & 0 & no & excellent & pretty well satisfied & large city\\
\hline
1972 & 27 & female & 0 & no & good & not satisfied at all & large city\\
\hline
1972 & 61 & female & 0 & no & good & pretty well satisfied & unknown\\
\hline
1972 & 30 & female & 2 & no & fair & not satisfied at all & unknown\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\begin{tabular}{l|l}
\hline
happy & degree\\
\hline
not too happy & less than high school\\
\hline
happy & high school\\
\hline
not too happy & bachelor's\\
\hline
happy & high school\\
\hline
happy & high school\\
\hline
\end{tabular}
\end{table}

\begin{itemize}
\tightlist
\item
  year: This variable indicates the year in which the data was
  collected. In this data-set, all the observations are from the year
  1972 to 2012.
\item
  age: This variable indicates the age of the individual at the time the
  data was collected. It is a continuous variable measured in years.
\item
  sex: This variable indicates the biological sex of the individual. It
  is a categorical variable with two levels: male and female.
\item
  babies: This variable indicates the number of babies the individual
  had at the time the data was collected. It is a categorical variable
  with different levels, depending on the number of babies: 0, 1, 2, 3,
  4, or 5+.
\item
  divorce: This variable indicates whether or not the individual had
  ever been divorced at the time the data was collected. It is a
  categorical variable with two levels: yes and no.
\item
  health: This variable indicates the self-reported health status of the
  individual at the time the data was collected. It is a categorical
  variable with different levels, depending on the health status:
  excellent, good, fair, or poor.
\item
  finance\_satisfied: This variable indicates the individual's level of
  satisfaction with their current financial situation. It is a
  categorical variable with different levels of satisfaction: very
  satisfied, more or less satisfied, not very satisfied, and not at all
  satisfied.
\item
  living\_area: This variable indicates the type of living area in which
  the individual resided at the time the data was collected. It is a
  categorical variable with different levels: large city, small city,
  suburban, and rural.
\item
  happy: This variable indicates the individual's level of happiness or
  life satisfaction. It is a categorical variable with different levels
  of happiness: very happy, pretty happy, not too happy, and not at all
  happy.
\end{itemize}

In Figure~\ref{fig-one}, this chart shows the number of people who are
very happy, not too happy, and happy. Overall, the data indicates that
the largest number of people are happy, with approximately 15,000
individuals falling into this category. On the other hand, the smallest
number of people are not too happy, with significantly fewer individuals
in this category compared to the other two variables. In summary, the
data suggests that the number of unhappy individuals is a relatively
small group.

@@

\caption{\label{fig-one}Couning of Happiness}

@@

\hypertarget{baby}{%
\subsubsection{Baby}\label{baby}}

In Figure~\ref{fig-two}, through the graph showing the relationship
between the number of children and happiness in the family, it is
obvious that when people have no children, the largest number of `very
happy', `pretty happy', and `not too happy' are shown. Although The
preliminary judgment is that the number of people who are happy without
children is the largest. But among the data, the data collected without
children is the most. In order to ensure the accuracy of the data, it is
necessary to further analyze the proportion of the number of children in
the family for the next part of the analysis.

@@

\caption{\label{fig-two}Relationship between Number of Babies and
Happiness}

@@

In Figure~\ref{fig-three}, which to provide a more detailed and
comprehensive view of the data, the chart displays an analysis and
visualization of the number of children had each year from 1972 to 2012,
in relation to the level of happiness. In regards to the variable ``not
too happy,'' the proportion of individuals who reported feeling unhappy
was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the
other hand, in regards to the variable ``happy,'' the percentage of
individuals reporting feeling happy was relatively high in 1973, 1977,
1994, 2006, and 2012.

@@

\hypertarget{health}{%
\subsubsection{Health}\label{health}}

In Figure~\ref{fig-four}, which represents the relationship between
participants' self-rated health and their self-rated level of happiness.
The chart shows that the proportion of participants who rated themselves
as ``very happy'' was the highest among those who rated their health as
``excellent''. On the other hand, the proportion of participants who
rated themselves as ``not too happy'' was the lowest among those who
rated their health as ``poor''.From the overall trend, it can be
inferred that the higher the participants' self-rated health, the higher
their self-rated level of satisfaction with life.

@@

\caption{\label{fig-four}Relationship between Health and Happiness}

@@

In Figure~\ref{fig-five}, which spanning from 1970 to 2010, illustrates
the relationship between participants' self-reported happiness levels
and their health states. It is evident that when participants rated
their health as `poor', the proportion of those who identified as `very
happy' was notably lower compared to other health states. On the other
hand, when participants reported their health as `excellent' or `good',
the number of `very happy' responses regarding their life satisfaction
increased significantly. In summary, this chart suggests a positive
correlation between people's health and their happiness in life.

@@

\caption{\label{fig-five}Relationship between Health and ``Very Happy''
With Year}

@@

\hypertarget{financial-satisfaction}{%
\subsubsection{Financial Satisfaction}\label{financial-satisfaction}}

In Figure~\ref{fig-six}, the graph depicts the relationship between
people's satisfaction with their financial situation and their
happiness.It is clear that when people are not very satisfied with their
current finances, the proportion of unhappy people in their lives is the
highest. On the other hand, when people are very satisfied with their
finances, the proportion of happy people in their lives is the highest,
and the proportion of unhappy people is also the lowest. Therefore, it
can be concluded that there is a positive relationship between people's
satisfaction with their current financial situation and their level of
happiness in life.

@@

\hypertarget{divorce}{%
\subsubsection{Divorce}\label{divorce}}

In Figure~\ref{fig-seven}, the graph represents the level of happiness
in life for individuals in two different states: divorced or married.
The graph shows that the levels of happiness in both marital states are
almost similar. However, the proportion of people who feel ``not too
happy'' in their lives is slightly higher among the divorced group than
among the married group. In conclusion, being divorced may have a slight
impact on one's level of happiness in life, with a small proportion of
individuals feeling ``not too happy.''

{\centering \includegraphics{paper_files/figure-pdf/fig-seven-1.pdf}

\caption{\label{fig-seven}Relationship between Happiness and Divorce}

In Figure~\ref{fig-eight}, which based on the analysis of the charts, it
appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010,
individuals who reported being divorced also reported a higher
percentage of happy responses. On the other hand, for the years 1976,
1980, 1984, 1987, 1989, and 2006, individuals who reported being married
reported a higher percentage of happy responses. Additionally, the
percentage of individuals who reported ``not too happy'' was
significantly higher for individuals who reported being divorced than
for those who reported being married in the years 1973, 1984, 1987,
1990, 1991, 1993, 2008, and 2012.

{\centering \includegraphics{paper_files/figure-pdf/fig-eight-1.pdf}

\caption{\label{fig-eight}Relationship between Divorce and Happiness by
Year}

\hypertarget{degree}{%
\subsubsection{Degree}\label{degree}}

In Figure~\ref{fig-nine}, which shows that there is a certain
relationship between people's level of education and their level of
happiness in life. From the graph, it can be observed that the
proportion of people who feel ``not too happy'' is the highest among
those with education levels lower than high school. However, the
proportion of unhappy individuals is the lowest among those with
bachelor's and graduate degrees, suggesting that as people's education
level increases, their level of happiness also gradually increases.

{\centering \includegraphics{paper_files/figure-pdf/fig-nine-1.pdf}

\caption{\label{fig-nine}Relationship between Happiness and Degree}

\hypertarget{model}{%
\section{Model}\label{model}}

\begin{verbatim}

Call:
lm(formula = happy_score ~ age + degree + finance_satified + 
    health + divorce, data = data)

Coefficients:
                          (Intercept)                                    age  
                             4.951478                              -0.002144  
                     degreebachelor's                         degreegraduate  
                             0.028053                               0.026886  
                    degreehigh school            degreeless than high school  
                            -0.005915                              -0.106730  
 finance_satifiednot satisfied at all  finance_satifiedpretty well satisfied  
                            -0.471882                               0.087194  
                           healthfair                             healthgood  
                            -0.315050                              -0.063929  
                           healthpoor                             divorceyes  
                            -0.747780                              -0.018373  
\end{verbatim}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}

  \newcolumntype{d}{S[
    input-open-uncertainty=,
    input-close-uncertainty=,
    parse-numbers = false,
    table-align-text-pre=false,
    table-align-text-post=false
  ]}

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being},
  pdfauthor={SHAOHAN CHANG},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Examining the Multifaceted Impact of Family Size on Happiness,
Health, Gender Dynamics, and Financial Well-being\thanks{Code and data
are available at: https://github.com/lucas11333/Of\_Wellbeing}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Cross-Sectional Cumulative Analysis of U.S. Microdata from
1972-2012}
\author{SHAOHAN CHANG}
\date{6 April 2023}

\begin{document}
\maketitle
\begin{abstract}
This study explores the multifaceted impact of family size on happiness,
health, gender dynamics, and financial well-being by analyzing
cross-sectional cumulative microdata from the United States between 1972
and 2012. This study analyzed the relationship between family size,
measured by the number of children, and various aspects of family life,
such as happiness, health, and financial satisfaction. The findings
suggest that happiness levels are highest among childless individuals,
while families with one child report the best health status.
Additionally, higher financial satisfaction is associated with fewer
children in a family. These insights matter as they provide a better
understanding of the factors influencing family size and the potential
consequences of family planning decisions on overall wellbeing.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, frame hidden, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

@@

This research investigates the diverse effects of family size on various
aspects such as happiness, health, gender roles, and financial
stability. The impact of the number of children in a family on various
aspects of family life has been a topic of interest for researchers and
policymakers alike (Brown 2010). Family size and structure play a
crucial role in shaping the lives of individuals and communities.
Understanding the connections between the number of children and factors
such as happiness, health, sex distribution, and financial satisfaction
can help inform decisions and policies aimed at promoting family
well-being (Cheng 2011).

In this context, the objective of this study is to explore the complex
interplay between family size and various aspects of family life. The
study employs cross-sectional cumulative micro data from the United
States spanning from 1972 to 2012. The paper aims to fill a gap in the
existing literature by providing a comprehensive analysis of the
relationship between the number of children in a family (0, 1, 2, 3, 4)
and different variables such as happiness, health, sex distribution, and
financial satisfaction, using multiple data sources. Previous research
on this topic has often focused on specific aspects of family life or
specific sub populations, leaving a gap in the understanding of the
broader relationships between family size and different variables.

The methodology of the study includes the analysis of several charts and
tables to uncover patterns and trends in the data, suggesting
connections between the number of children in a family and the variables
of interest. For example, the data reveals that families with better
health tend to have a higher likelihood of having one or more children,
while families with lower financial satisfaction tend to have more
children (Waite 1995). However, the relationships identified in this
study may not be linear, and it is important to consider the potential
influence of other factors on the number of children in a family.

The structure of the paper is as follows: first, we present the data and
methodology used in the study, followed by a detailed analysis of the
relationships between the number of children in a family and the
variables of interest. Next, we discuss the implications of the findings
and their relevance to broader discussions on family well-being and
policy. Finally, we conclude with a summary of the main findings and
suggestions for future research in this area.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

The data used for this study was obtained from cross-sectional
cumulative micro data from the United States, spanning from 1972 to
2012. Multiple data sources were utilized to ensure a comprehensive and
representative sample of the US population. These data sources include
the General Social Survey (GSS), such as happiness, health, gender
roles, and financial stability.The sample for this study consists of
families with different numbers of children (0, 1, 2, 3, 4). The final
sample size was determined by considering the availability of data and
the need for a balanced representation of different family sizes. The
sample includes families from diverse socioeconomic backgrounds,
ethnicities, and geographic locations in the United States, ensuring a
comprehensive representation of the population.

@@

Used some R language packages, such as tidyverse (Wickham et al. 2019),
dplyr (Wickham et al. 2023), janitor (Firke 2023) , knitr (Xie 2014),
here (Müller 2020), haven (Wickham, Miller, and Smith 2022), ggplot
(Wickham 2016) , kableExtra (Zhu 2021) , model summary (Arel-Bundock
2022) to assist in data analysis, and the data from General Social
Survey ({``GSS General Social Survey''} 2023).

\hypertarget{data}{%
\subsection{Data}\label{data}}

The following table shows the first five rows of data and their
corresponding parameters.The following data section provides a more
detailed explanation of the selected variables for the data.

In Table~\ref{tbl-var} contains information on various personal and
demographic characteristics of individuals, collected between the years
1972 and 2012. The data-set comprises of 10 variables, namely age, sex,
number of babies, divorce status, self-reported health status, financial
satisfaction, level of happiness, and additional variables. The data-set
contains 38,960 rows, providing ample opportunities to analyze the
relationships between these variables and gain valuable insights into
the factors that could potentially impact an individual's overall life
satisfaction.

\hypertarget{tbl-var}{}
\begin{table}
\caption{\label{tbl-var}Report Data (First 5 rows) }\tabularnewline

\centering
\begin{tabular}{r|l|r|l|l|l}
\hline
year & sex & babies & health & finance\_satified & happy\\
\hline
1972 & male & 2 & fair & pretty well satisfied & very happy\\
\hline
1972 & female & 1 & good & not satisfied at all & very happy\\
\hline
1972 & female & 1 & excellent & not satisfied at all & very happy\\
\hline
1972 & male & 1 & good & pretty well satisfied & very happy\\
\hline
1972 & male & 2 & excellent & more or less satisfied & not too happy\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\begin{tabular}{r|r|r|r}
\hline
happy\_score & health\_score & finance\_score & babies\_number\\
\hline
3 & 2 & 3 & 2\\
\hline
3 & 3 & 4 & 1\\
\hline
3 & 4 & 4 & 1\\
\hline
3 & 3 & 3 & 1\\
\hline
0 & 4 & 2 & 2\\
\hline
\end{tabular}
\end{table}

\begin{itemize}
\tightlist
\item
  year: This variable indicates the year in which the data was
  collected. In this data-set, all the observations are from the year
  1972 to 2012.
\item
  sex: This variable indicates the biological sex of the individual. It
  is a categorical variable with two levels: male and female.
\item
  babies: This variable indicates the number of babies the individual
  had at the time the data was collected. It is a categorical variable
  with different levels, depending on the number of babies: 0, 1, 2, 3,
  4, or 5+.
\item
  health: This variable indicates the self-reported health status of the
  individual at the time the data was collected. It is a categorical
  variable with different levels, depending on the health status:
  excellent, good, fair, or poor.
\item
  finance\_satisfied: This variable indicates the individual's level of
  satisfaction with their current financial situation. It is a
  categorical variable with different levels of satisfaction: very
  satisfied, more or less satisfied, not very satisfied, and not at all
  satisfied.
\item
  happy: This variable indicates the individual's level of happiness or
  life satisfaction. It is a categorical variable with different levels
  of happiness: very happy, pretty happy, not too happy, and not at all
  happy.
\item
  happy\_score: The happy\_score variable is an ordinal variable
  representing the self-reported happiness levels of the individuals in
  the dataset. It ranges from 0 to 3, with 0 representing ``not too
  happy,'' 1 representing ``happy,'' 2 representing ``very happy,'' and
  3 reserved for any unclassified or missing responses.
\item
  health\_score: The health\_score variable is an ordinal variable
  indicating the self-reported health status of the individuals in the
  dataset. It ranges from 1 to 4, with 1 denoting ``poor'' health, 2
  signifying ``fair'' health, 3 representing ``good'' health, and 4
  referring to ``excellent'' health. The value 5 is reserved for any
  unclassified or missing responses.
\item
  finance\_score: This ordinal variable represents the financial
  satisfaction level of the individuals in the dataset. It ranges from 1
  to 3, with 1 indicating ``Not at all satisfied,'' 2 denoting ``more or
  less satisfied,'' and 3 signifying ``pretty well satisfied.'' The
  value 4 is reserved for any unclassified or missing responses.
\item
  babies\_number: The babies\_number variable is an ordinal variable
  denoting the number of babies an individual in the dataset has. It
  ranges from 0 to 4, where 0 represents ``0'' babies, 1 denotes ``1''
  baby, 2 signifies ``2'' babies, 3 indicates ``3'' babies, and 4 refers
  to ``4'' babies. The value 5 is reserved for any unclassified or
  missing responses.
\end{itemize}

In this study, missing values (NA) have not been removed. The rationale
behind this decision is that eliminating missing values from every
column would lead to a significant reduction in the data set's size,
compromising its representatives. Instead, R is employed to
automatically filter out missing values, ensuring data integrity.

\hypertarget{exploring-the-connection-between-childlessness-and-happiness}{%
\subsubsection{Exploring the Connection Between Childlessness and
Happiness}\label{exploring-the-connection-between-childlessness-and-happiness}}

In Figure~\ref{fig-one},which analysis explores the relationship between
the number of children in a family and happiness levels, categorized as
`very happy,' `pretty happy,' and `not too happy.' Although childless
families show the highest numbers in each happiness category, the data
collected for such families is more abundant, necessitating an analysis
of happiness proportions within each family size. The findings reveal no
linear correlation between the number of children and overall family
happiness, with happiness varying across family sizes without a
consistent pattern. The non-uniform distribution of happiness categories
among families with different numbers of children implies that factors
beyond the number of children also contribute to happiness levels. In
conclusion, the data shows variations in happiness levels among families
of different sizes but does not establish a definitive correlation
between the number of children and overall family happiness. Further
research is needed to better understand the complex factors influencing
happiness within families.

@@

\caption{\label{fig-one}Relationship between Number of Babies and
Happiness}

@@

In Figure~\ref{fig-two},which presented in the table indicates that the
sex distribution varies depending on the number of babies in the family.
A higher percentage of females compared to males is consistently
observed across all groups. The lowest difference in sex distribution is
found among families with no babies, where the female-to-male ratio is
relatively closer. As the number of babies in a family increases, the
percentage of females also increases, with the highest difference
observed in families with one and four babies. In these groups, the sex
distribution is more skewed towards females.

@@

\caption{\label{fig-two}Relationship between Number of Babies and
Gender}

@@

In Figure~\ref{fig-three}, which to provide a more detailed and
comprehensive view of the data, the chart displays an analysis and
visualization of the number of children had each year from 1972 to 2012,
in relation to the level of happiness. In regards to the variable ``not
too happy,'' the proportion of individuals who reported feeling unhappy
was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the
other hand, in regards to the variable ``happy,'' the percentage of
individuals reporting feeling happy was relatively high in 1973, 1977,
1994, 2006, and 2012.From the overall data, it can be seen that when
people have 1 or 2 children, the most common self-rated health statuses
are excellent, fair, and good.

@@

\hypertarget{the-relationship-between-number-of-children-and-self-rated-health-status}{%
\subsubsection{The Relationship Between Number of Children and
Self-Rated Health
Status}\label{the-relationship-between-number-of-children-and-self-rated-health-status}}

In Figure~\ref{fig-four}, which observed that when individuals have one
child, there is a significantly higher proportion of participants who
rate their health as `good' or `excellent' compared to other categories.
In contrast, for participants who do not have any children, the
proportion of those who rate their health as `poor' is the highest, but
no clear conclusion can be drawn from this finding. For individuals with
three children, the feedback on their health status is evenly
distributed among `good', `fair', and `excellent', with a very small
proportion of participants reporting `poor' health. Overall, having one
child is associated with the highest proportion of participants
reporting `excellent' health status.

@@

\caption{\label{fig-four}Number of Children and Self-Rated Health
Status}

@@

In Figure~\ref{fig-five}, which present the dot plot, which represent
the each number of babies in different condition of health, which
explores the relationship between health and the number of babies in the
family. The data is organized into four health categories - `excellent',
`fair', `good', and `poor' - and five categories based on the number of
babies, ranging from 0 to 4.The data reveals a pattern suggesting a
connection between health status and the number of babies in a family.
Families with `excellent' health have a more balanced distribution of
babies, with a higher proportion of families having one or two babies
compared to those with poorer health. This trend indicates that better
health is associated with a higher likelihood of having one or more
babies.As the number of babies increases, the percentages for all four
health categories tend to decrease. This pattern is most noticeable in
the `poor' health category, where the decline in percentages is more
pronounced as the number of babies increases.In summary, the data
suggests a relationship between health and the number of babies in a
family. Better health is generally associated with a higher likelihood
of having one or more babies, while poorer health tends to correlate
with a lower likelihood. However, it is essential to consider that the
relationship may not be linear and that other factors could also
influence the number of babies in a family.

@@

\caption{\label{fig-five}Relationship between Health and Number of
Babies With Year}

@@

\hypertarget{the-association-between-family-size-and-financial-satisfaction}{%
\subsubsection{The Association Between Family Size and Financial
Satisfaction}\label{the-association-between-family-size-and-financial-satisfaction}}

In Figure~\ref{fig-six}, which appears that the number of babies in a
family is related to the level of financial satisfaction. In general,
families with lower financial satisfaction, regardless of the category,
tend to have a higher number of babies. This trend is observed across
all three financial satisfaction levels.It is interesting to note that
the majority of families in all financial satisfaction levels have 0
babies. However, the percentage of families with 0 babies is notably
higher in the `pretty well satisfied' category compared to the `more or
less satisfied' and `not satisfied at all' categories.As the number of
babies increases, the percentages for all three financial satisfaction
categories tend to decrease. This pattern is more pronounced in the
`pretty well satisfied' category, where the decline in percentages is
steeper as the number of babies increases.In summary, the data suggests
a connection between financial satisfaction and the number of babies in
a family. Families with higher financial satisfaction generally have
fewer babies, while those with lower financial satisfaction have more
babies. It is essential to consider that this relationship may not be
linear, and other factors could also influence the number of babies in a
family.

@@

\hypertarget{model-linear-regression}{%
\section{Model : Linear Regression}\label{model-linear-regression}}

\begin{equation}\protect\hypertarget{eq-model}{}{
\hat{Y}=\hat{\beta_0} + \hat{\beta_1}X_{finance-score} + \hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
\hat{\beta_6}X_{babies-number} 
}\label{eq-model}\end{equation}

\hypertarget{tbl-lm}{}
\begin{table}
\caption{\label{tbl-lm}Linear Model and its Summary Statistics }\tabularnewline

\centering
\begin{tabular}[t]{lc}
\toprule
  & Babies\\
\midrule
(Intercept) & \num{1.24}\\
 & {}[\num{1.10}, \num{1.37}]\\
finance\_score & \num{0.03}\\
 & {}[\num{0.01}, \num{0.06}]\\
health\_score & \num{0.02}\\
 & {}[\num{-0.01}, \num{0.05}]\\
happyvery happy & \num{0.01}\\
 & {}[\num{-0.05}, \num{0.06}]\\
\midrule
Num.Obs. & \num{3047}\\
R2 & \num{0.002}\\
R2 Adj. & \num{0.001}\\
AIC & \num{5686.7}\\
BIC & \num{5716.8}\\
Log.Lik. & \num{-2838.336}\\
F & \num{2.129}\\
RMSE & \num{0.61}\\
\bottomrule
\end{tabular}
\end{table}

The Table~\ref{tbl-lm} is built based on the Equation~\ref{eq-model}:

\begin{itemize}
\tightlist
\item
  \(\hat{Y}\) is predicted value of the dependent variable. This is the
  outcome we're trying to predict or estimate based on the independent
  variables.
\item
  \(\hat{\beta_0}\) : The intercept term, which represents the expected
  value of \(\hat{Y}\) when all independent variables are equal to 0.
\item
  \(\hat{\beta_1}\) , \(\hat{\beta_2}\) , \(\hat{\beta_3}\) are the
  estimated coefficients for each independent variable. These
  coefficients indicate the average change in the dependent variable
  \(\hat{Y}\) associated with a one-unit change in the corresponding
  independent variable, holding all other variables constant. The
  independent variables are:
\item
  \(X_{age}\) : Age of the individual.
\item
  \(X_{degree-score}\) : A measure of the individual's level of
  education or degree.
\item
  \(X_{finance-score}\) : A measure of the individual's financial
  stability or status.
\item
  \(X_{health-score}\) : A measure of the individual's overall health.
\item
  \(X_{divorce-score}\) : A measure of the individual's likelihood of
  divorce or past divorces.
\item
  \(X_{babies-number}\) : The number of babies/children the individual
  has.
\end{itemize}
